Spatial Reasoning and Statistical Graphics

### 2014-10-20 Paper/Draft1/TestingVisualAptitude.Rnw
Label RA tests in appendix

\section*{Appendix}
\renewcommand{\thesubsection}{\Alph{subsection}}
\subsection{Examining potential testing biases}
T-tests of results for Hillary and Stephanie: 
<<ttest, echo=F, include=T, results='asis'>>=
ans.summary$tester <- c(rep("Hillary", 18), rep("Stephanie", nrow(ans.summary)-18))
card.rotation <- t.test(card_rot~tester, data=ans.summary)
paper.folding <- t.test(folding~tester, data=ans.summary)
fig.class <- t.test(fig_class~tester, data=ans.summary)
lineup <- t.test(lineup~tester, data=ans.summary)

>>>>

\section*{Appendix}
\renewcommand{\thesubsection}{\Alph{subsection}}
\subsection{Examining potential testing biases}\label{app:ratests}
T-tests of results for Hillary and Stephanie: 
<<ttest, echo=F, include=T, results='asis'>>=
ans.summary$tester <- c(rep("Hillary", 18), rep("Stephanie", nrow(ans.summary)-18))
card.rotation <- t.test(card_rot~tester, data=ans.summary)
paper.folding <- t.test(folding~tester, data=ans.summary)
fig.class <- t.test(fig_class~tester, data=ans.summary)
lineup <- t.test(lineup~tester, data=ans.summary)
